Gammapy: A Python package for gamma-ray astronomy

### 2023-08-23 src/ms-review.tex
Add declaration of contributions

        We would like to thank the \texttt{Numpy}, \texttt{Scipy}, \texttt{IPython} and
        \texttt{Matplotlib} communities for providing their packages which are
        invaluable to the development of \gammapy. We thank the \github team for
        providing us with an excellent free development platform. We also are grateful
        to Read the Docs (\ReadthedocsUrl), and Travis (\TravisUrl) for providing free
        documentation hosting and testing respectively. A special acknowledgment has to be given
        to our first Lead Developer of \gammapy, Christoph Deil. Finally, we would like to thank
        all the \gammapy users that have provided feedback and submitted bug reports.

@@

>>>>

        We would like to thank the \texttt{Numpy}, \texttt{Scipy}, \texttt{IPython} and
        \texttt{Matplotlib} communities for providing their packages which are
        invaluable to the development of \gammapy. We thank the \github team for
        providing us with an excellent free development platform. We also are grateful
        to Read the Docs (\ReadthedocsUrl), and Travis (\TravisUrl) for providing free
        documentation hosting and testing respectively. Finally, we would like to thank
        all the \gammapy users that have provided feedback and submitted bug reports.

@@

        A special acknowledgment has to be given to our first lead developer, Christoph Deil, who
        started the \gammapy project and set the foundation for its future success.

        A. Donath, R. Terrier, Q. Remy, A. Sinha, C. Nigro, F. Pintore, B. Khélifi, L. Olivera-Nieto, J. E. Ruiz,
        K. Brügge, M. Linhoff and J.L. Contreras contributed to the writing of the manuscript.

        A. Donath, B. Khélifi, C. Boisson, C.Deil, C. van Eldik, D. Berge, E. de Ona Wilhelmi, F. Acero, F. Pintore,
        M. Cardillo, J. Hinton, J.L. Contreras, M. Fuessling, R. Terrier, R. Zanin, R. López-Coto and S. Funk
        are current or former members of the Gammapy coordination committee and contributed to promotion, coordination
        and steering of the \gammapy project.

        A. Aguasca-Cabot, P. Bhattacharjee, K. Brügge, J. Buchner, D. Carreto Fidalgo, A. Chen, M. de Bony de Lavergne,
        A. Donath, J. V. de Miranda Cardoso, C. Deil, L. Giunti, L. Jouvin, B. Khélifi, J. King, J. Lefaucheur,
        M. Lemoine-Goumard, J.P. Lenain, M. Linhoff, L. Mohrmann, D. Morcuende, C. Nigro, L. Olivera-Nieto,
        S. Panny, M. Regeard, Q. Remy, J. E. Ruiz, L. Saha, H. Siejkowski, A. Siemiginowska, A. Sinha,
        B. M. Sipőcz, R. Terrier, T. Unbehaun, T. Vuillaume contributed to the code development of \gammapy.
